A Study of the Effectiveness of Usage Examples in REST API Documentation

### 2017-07-21 controlled_study/controlled_study.tex
controlled study paper is wholly included
boxes look good

\section{abstract}
Generating and maintaining REST API documentation with usage examples can be a time consuming and expensive process for evolving APIs. Most REST API documentation tools focus on automating the documentation of the API objects, but require manual effort for capturing usage examples. Consequently, REST API developers need to know the cost vs. benefit of providing usage examples in the documentation to prioritize the documentation efforts. To this end, we have performed a controlled study with 26 experienced software engineers to understand problems that REST API client developers face while using an API without usage examples. We found that REST API client developers face productivity problems with using correct data types, data formats, required HTTP headers and request body when documentation lacks usage examples. By following the REST API documentation suggestions from this paper, REST API developers can reduce the errors, improve success rate and satisfaction of API client developers.

@@

\begin{figure}[h!]
  \begin{center}
    \includegraphics[width=\linewidth,keepaspectratio]{schema.png}
  \end{center}
  \caption{Screenshot of documentation for Post/date}
  \label{fig:schema}
\end{figure}

@@

\begin{table}[!tbh]
  \caption{Participant Profile}
  \label{table:participants}

\begin{tabular}{|p{0.8in} p{.6in} p{0.7in} p{0.7in}|}

@@

\begin{subfigure}[t]{4in}
\centering
\includegraphics[width=4in]{original.png}
\caption{Original API Documentation}
\label{fig:original}
\end{subfigure}
~
\begin{subfigure}[t]{3in}
\centering
\includegraphics[width=2.7in]{forked.png}
\caption{API Documentation Enhanced with an Example}
\label{fig:enhanced}
\end{subfigure}
\caption{Screenshots of Original vs. Enhanced API Documentation}
\end{figure*}

@@

\pgfplotsset{compat=1.14}
\usetikzlibrary{patterns}
\pgfplotstableread[col sep=comma]{groupone.csv}\groupone

\begin{figure*}[htb]

\begin{subfigure}[b]{0.5\textwidth}
\centering
\begin{tikzpicture}
    \begin{axis}[
        ybar,
        xtick=data,
        xticklabels from table={\groupone}{Task},
        legend style={at={(0.5,-0.15)},
        anchor=north,legend columns=-1},
        ylabel=Avg. Trial API Calls (Frequency),
        width=2.8in
    ]
    \addplot[pattern=crosshatch dots, pattern color=gray] table [col sep=comma, x expr=\coordindex, y=AverageAPICalls] {groupone.csv};
    \addplot[draw=black] table [col sep=comma, x expr=\coordindex, y=AverageAPICalls] {grouptwo.csv};
    \legend{G1 Avg. Trial API Calls, G2 Avg. Trial API Calls}
    \end{axis}

    \addplot[smooth,mark=*,black] table [col sep=comma, x expr=\coordindex, y=SuccessRate] {grouptwo_success.csv};
      \addlegendentry{G2 Success Rate}
    \end{axis}
\end{tikzpicture}
\caption{Trial vs. Successful API Calls}
\label{graph:productivity}
\end{subfigure}
\begin{subfigure}[b]{0.4\textwidth}
\centering
\begin{tikzpicture}
    \begin{axis}[
        ybar,
        xtick=data,
        xticklabels from table={\groupone}{Task},
        legend style={at={(0.5,-0.15)},
        anchor=north,legend columns=-1},
        ylabel=Avg. Time Spent (minutes),
        width=2.8in
    ]
    \addplot[pattern=crosshatch dots, pattern color=gray] table [col sep=comma, x expr=\coordindex, y=Time] {groupone_time.csv};
    \addplot[draw=black] table [col sep=comma, x expr=\coordindex, y=Time] {grouptwo_time.csv};
    \legend{G1 Avg. Time Spent, G2 Avg. Time Spent}
    \end{axis}

@@

@@

\hspace{-5mm}
\fbox{
\begin{minipage}{0.95\linewidth}

@@

\end{minipage}
}
\vspace{0.5mm}

@@

\vspace{1mm}
\hspace{-5mm}
\fbox{
\begin{minipage}{0.95\linewidth}

\textbf{Recommendation 2.} REST API developers need to include examples showing the valid data format for the API elements.
\end{minipage}
}
\vspace{0.5mm}

@@

\vspace{1mm}
\hspace{-5mm}
\fbox{
\begin{minipage}{0.95\linewidth}

\textbf{Recommendation 3.} If API requests need to use HTTP Request headers, in addition to the request method and body, REST API develpers need to include examples of the HTTP headers.
\end{minipage}
}
\vspace{0.5mm}

@@

\vspace{1mm}
\hspace{-5mm}
\fbox{
\begin{minipage}{0.95\linewidth}

\textbf{Recommendation 4.} If there are prerequisites for making an API call, REST API developers need to provide examples showing how to get the prerequisites in the API documentation.
\end{minipage}
}
\vspace{0.5mm}

@@

\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,refs}

%\end{document}

>>>>

\section{Abstract}
Generating and maintaining REST API documentation with usage examples can be a time consuming and expensive process for evolving APIs. Most REST API documentation tools focus on automating the documentation of the API objects, but require manual effort for capturing usage examples. Consequently, REST API developers need to know the cost vs. benefit of providing usage examples in the documentation to prioritize the documentation efforts. To this end, we have performed a controlled study with 26 experienced software engineers to understand problems that REST API client developers face while using an API without usage examples. We found that REST API client developers face productivity problems with using correct data types, data formats, required HTTP headers and request body when documentation lacks usage examples. By following the REST API documentation suggestions from this paper, REST API developers can reduce the errors, improve success rate and satisfaction of API client developers.

@@

\begin{figure}
  \begin{center}
    \fbox{\includegraphics[width=\linewidth,keepaspectratio]{schema.png}}
  \end{center}
  \caption{Screenshot of documentation for Post/date}
  \label{fig:schema}
\end{figure}

@@

\begin{table}[!tbh]
  \centering
  \caption{Participant Profile}
  \label{table:participants}

  \begin{tabular}{|p{1.5in} p{1in} p{1.5in} p{1.5in}|}

@@

\begin{subfigure}[t]{5in}
\centering
\includegraphics[width=5in]{original.png}
\caption{Original API Documentation}
\label{fig:original}
\end{subfigure}
~
\begin{subfigure}[t]{5in}
\centering
\includegraphics[width=5in]{forked.png}
\caption{API Documentation Enhanced with an Example}
\label{fig:enhanced}
\end{subfigure}
\caption{Screenshots of Original vs. Enhanced API Documentation}
\end{figure*}

@@

@@

\pgfplotsset{compat=1.14}
\usetikzlibrary{patterns}
\pgfplotstableread[col sep=comma]{controlled_study/groupone.csv}\groupone

\begin{figure*}[!h]

\begin{subfigure}[b]{\textwidth}
\centering
\begin{tikzpicture}
    \begin{axis}[
        ybar,
        xtick=data,
        xticklabels from table={\groupone}{Task},
        legend style={at={(0.5,-0.15)},
        anchor=north,legend columns=-1},
        ylabel=Avg. Trial API Calls (Frequency),
        width=2.8in
    ]
    \addplot[pattern=crosshatch dots, pattern color=gray] table [col sep=comma, x expr=\coordindex, y=AverageAPICalls] {groupone.csv};
    \addplot[draw=black] table [col sep=comma, x expr=\coordindex, y=AverageAPICalls] {grouptwo.csv};
    \legend{G1 Avg. Trial API Calls, G2 Avg. Trial API Calls}
    \end{axis}

    \addplot[smooth,mark=*,black] table [col sep=comma, x expr=\coordindex, y=SuccessRate] {grouptwo_success.csv};
      \addlegendentry{G2 Success Rate}
    \end{axis}
\end{tikzpicture}
\caption{Trial vs. Successful API Calls}
\label{graph:productivity}
\end{subfigure}
\begin{subfigure}[b]{\textwidth}
\centering
\begin{tikzpicture}
    \begin{axis}[
        ybar,
        xtick=data,
        xticklabels from table={\groupone}{Task},
        legend style={at={(0.5,-0.15)},
        anchor=north,legend columns=-1},
        ylabel=Avg. Time Spent (minutes),
        width=2.8in
    ]
    \addplot[pattern=crosshatch dots, pattern color=gray] table [col sep=comma, x expr=\coordindex, y=Time] {groupone_time.csv};
    \addplot[draw=black] table [col sep=comma, x expr=\coordindex, y=Time] {grouptwo_time.csv};
    \legend{G1 Avg. Time Spent, G2 Avg. Time Spent}
    \end{axis}

@@

\vspace{10mm}
\hspace{-5mm}
\fbox{
\begin{minipage}{0.95\linewidth}

@@

\end{minipage}
}
\vspace{10mm}

@@

\vspace{10mm}
\hspace{-5mm}
\fbox{
\begin{minipage}{0.95\linewidth}

\textbf{Recommendation 2.} REST API developers need to include examples showing the valid data format for the API elements.
\end{minipage}
}
\vspace{10mm}

@@

\vspace{10mm}
\hspace{-5mm}
\fbox{
\begin{minipage}{0.95\linewidth}

\textbf{Recommendation 3.} If API requests need to use HTTP Request headers, in addition to the request method and body, REST API develpers need to include examples of the HTTP headers.
\end{minipage}
}
\vspace{10mm}

@@

\vspace{10mm}
\hspace{-5mm}
\fbox{
\begin{minipage}{0.95\linewidth}

\textbf{Recommendation 4.} If there are prerequisites for making an API call, REST API developers need to provide examples showing how to get the prerequisites in the API documentation.
\end{minipage}
}
\vspace{10mm}

@@

\bibliographystyle{IEEEtran}
\bibliography{controlled_study/IEEEabrv,controlled_study/refs}
